A systematic search for transiting planets using \KT

### 2015-02-06 ms.tex
nothing really
words about posterior sampling

After running these light curves with injections through the full pipeline, if
the resulting period and phase of the recovered signal were within YYYY of the
true injected values, we deemed the injection a success.
Figure ZZZZ shows the fraction of recovered signals as a function of the
physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.

@@

\subsection{Planet candidates}

\subsection{Probable binaries}

>>>>

After running these light curves with injections through the full pipeline, if
the resulting period and phase of the recovered signal were within YYYY of the
true injected values, we deemed the injection a success.
\Fig{completeness} shows the fraction of recovered signals as a function of the
physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.

@@

After running the 21XXX light curves through our full pipeline, we end up
with XXXX TCEs \dfmtodo{change this name} and after hand vetting, we are left
with YYYY convincing transiting candidates.
Of these candidates, ZZZ are probable binaries with obviously visible
secondary eclipses and we list these candidates in Table \dfmtodo{SOMETABLE}.
This leaves WWW planet candidates that are listed in Table
\dfmtodo{SOMETABLE}.

\paragraph{Posterior constraints on physical parameters}

To fit for the observable parameters of the transit signals in detail, we use
the same linear model for the systematics but then we combine this with a
physical transit model (M\&A, etc.).
Since this transit model is no longer linear, we use Markov Chain Monte Carlo
(MCMC; cite emcee) to draw posterior samples from this model.
At each step in the chain, we \emph{marginalize over the model of the
systematics}.
This means that we don't de-trend the data or make any hard decision about
the actual value of the systematics.
We sample the stellar density, limb-darkening coefficients, period, phase,
radius ratio, impact parameter, eccentricity, and argument of periapsis.
\dfmtodo{List priors.}
The quantiles of these posterior samplings are given in table \dfmtodo{some
table} and the full chains are available electronically \dfmtodo{some URL}.
